The Chemistry Development Kit (CDK): atom typing, rendering, molecular formulas, and substructure searching

### 2016-09-29 article.tex
Better organization of the figure/table part
Make runtimes in Table 5 consistent with Table 1

@@

  \subsection*{Table 1 - Evaluation of molecular formula generators.}
  \label{tab:formula_generators}
  The resulting formula counts and runtimes of the HR2, PFG, and CDK chemical
formula generators on two different inputs with two different mass tolerance
settings. For the set of small masses, $10\,000$ mass values in the range of
$0$--$500$ Da were randomly selected from the Global Natural Products Social
Molecular Networking database~\cite{wang2016}. For the set of large masses, $20$
mass values in the range of $1\,500$--$3\,500$ Da were randomly selected from the same
database. Formulas were generated using chemical elements C,H,N,O,P,S without
bounds (the allowed atom count was set to $0$--$10\,000$ for each element). All
heuristic filtering rules were disabled for the purpose of the evaluation. The
slight differences in the number of generated formulas were caused by different
isotope masses embedded in each software and/or by rounding errors during
calculation. The runtimes are average values from three independent runs
performed on three different 16-core Intel Xeon 2.9~GHz CPU workstations
equipped with 189~GB RAM, running Ubuntu Linux version 12.04.5 LTS and OpenJDK
Java runtime version 1.7.0\_101.
  \vskip 1\baselineskip

    \begin{minipage}{1\textwidth}
    \centering
    \begin{tabular}{llllllll}
	\multirow{2}{1in}{ Input } & \multirow{2}{1in}{ Mass tolerance ($\pm$ Da) } & \multicolumn{3}{c}{ \# of generated formulas } & \multicolumn{3}{c}{ Runtime (s) } \\
	& & HR2 & PFG & CDK & HR2 & PFG & CDK \\
	$10\,000$ small masses & $0.001$ & $616\,846$ & $616\,846$ & $616\,843$ & $669$ & $168$ & $\mathbf{41}$ \\
	$10\,000$ small masses & $0.01$ & $6\,163\,303$ & $6\,163\,302$ & $6\,163\,326$ & $689$ & $501$ & $\mathbf{212}$ \\
	$20$ large masses & $0.001$ & $4\,912\,939$ & $4\,912\,939$ & $4\,912\,904$ & $26\,370$ & $1\,292$ & $\mathbf{177}$ \\
	$20$ large masses & $0.01$ & $49\,128\,811$ & $49\,128\,810$ & $49\,128\,815$ & $26\,587$ & $3\,406$ & $\mathbf{1\,580}$ \\
    \end{tabular}
    \end{minipage}

@@

\begin{tabular}{lll}
Toolkit                   & Time   & Matched \\
\hline
CDK 1.4.9                 & 64m3s  & 69,782  \\
CDK \cdkversion{}         & 1m7s   & 62,518  \\
Open Babel 2.3.90         & 13m55s & 61,906  \\
RDKit 2016.3.4            & 6m18s  & 62,402  \\
\end{tabular}

>>>>

\clearpage

@@

  \subsection*{Table 1 - Evaluation of molecular formula generators.}
  \label{tab:formula_generators}
  The resulting formula counts and runtimes of the HR2, PFG, and CDK chemical
formula generators on two different inputs with two different mass tolerance
settings. For the set of small masses, 10,000 mass values in the range of
0--500 Da were randomly selected from the Global Natural Products Social
Molecular Networking database~\cite{wang2016}. For the set of large masses, 20
mass values in the range of 1,500--3,500 Da were randomly selected from the same
database. Formulas were generated using chemical elements C,H,N,O,P,S without
bounds (the allowed atom count was set to 0--10,000 for each element). All
heuristic filtering rules were disabled for the purpose of the evaluation. The
slight differences in the number of generated formulas were caused by different
isotope masses embedded in each software and/or by rounding errors during
calculation. The runtimes are average values from three independent runs
performed on three different 16-core Intel Xeon 2.9~GHz CPU workstations
equipped with 189~GB RAM, running Ubuntu Linux version 12.04.5 LTS and OpenJDK
Java runtime version 1.7.0\_101.
  \vskip 1\baselineskip

    \begin{minipage}{1\textwidth}
    \centering
    \begin{tabular}{llllllll}
	\multirow{2}{1in}{ Input } & \multirow{2}{1in}{ Mass tolerance ($\pm$ Da) } & \multicolumn{3}{c}{ \# of generated formulas } & \multicolumn{3}{c}{ Runtime (s) } \\
	& & HR2 & PFG & CDK & HR2 & PFG & CDK \\
	10,000 small masses & 0.001 & 616,846 & 616,846 & 616,843 & 669 & 168 & \textbf{41} \\
	10,000 small masses & 0.01 & 6,163,303 & 6,163,302 & 6,163,326 & 689 & 501 & \textbf{212} \\
	20 large masses & 0.001 & 4,912,939 & 4,912,939 & 4,912,904 & 26,370 & 1,292 & \textbf{177} \\
	20 large masses & 0.01 & 49,128,811 & 49,128,810 & 49,128,815 & 26,587 & 3,406 & \textbf{1,580} \\
    \end{tabular}
    \end{minipage}

@@

\begin{tabular}{lll}
Toolkit                   & Time (s)   & Matched \\
\hline
CDK 1.4.9                 & 3,843  & 69,782  \\
CDK \cdkversion{}         & 67   & 62,518  \\
Open Babel 2.3.90         & 835 & 61,906  \\
RDKit 2016.3.4            & 378  & 62,402  \\
\end{tabular}
